---
title: "Study-UI"
output: html_document
date: "2023-12-03"
---

Load CSV
```{r}
data <- read.csv("data.csv")
```



Preference Likert Scale
```{r}
library(reshape2)

selected_columns <- data[c("Learning", "Navigation", "Intuitiveness", "FClarity", "Efficiency", "Immersion", "Comfort")]

data_long <- melt(selected_columns)

rating_labels <- c("Strongly Prefer 3D UI", "Prefer 3D UI", "Neutral", "Prefer Flat UI", "Strongly Prefer Flat UI")

library(ggplot2)

plot <- ggplot(data_long, aes(x = variable, fill = factor(value))) +
  geom_bar(position = "fill") +
  coord_flip() +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_manual(name = "Rating", 
                    values = c("1" = "#e9505a", "2" = "#EBCCCE", "3" = "gray88", "4" = "#cfcfe8", "5" = "#7474b0"),
                    labels = rating_labels) +
  labs(x = "", y = "Percentage", title = "Likert Scale Ratings") +
  theme_minimal()

ggsave(filename = "visualized/preference_likert.png", plot = plot, width = 5, height = 2, dpi = 500)

plot
```

```{r}


# Load necessary libraries
library(ggplot2)
library(dplyr)


# Reordering factors as per the specified order
data$Video_game_exp <- factor(data$Video_game_exp, levels = c('Beginner', 'Casual', 'Intermediate', 'Advanced', 'Expert'))
data$VR_exp <- factor(data$VR_exp, levels = c('Novice', 'Beginner', 'Intermediate'))
data$Background_design_tech <- factor(data$Background_design_tech, levels = c('None', 'Some', 'Experienced'))

# Calculating mean tutorial and task times
video_game_exp_stats <- data %>% group_by(Video_game_exp) %>% summarise(Avg_Tutorial_Time = mean(Tutorial_time), Avg_Task_Time = mean(Task_time))
vr_exp_stats <- data %>% group_by(VR_exp) %>% summarise(Avg_Tutorial_Time = mean(Tutorial_time), Avg_Task_Time = mean(Task_time))
background_exp_stats <- data %>% group_by(Background_design_tech) %>% summarise(Avg_Tutorial_Time = mean(Tutorial_time), Avg_Task_Time = mean(Task_time))


# Plotting
# Video Game Experience
plot <- ggplot(video_game_exp_stats, aes(x=Video_game_exp, y=Avg_Tutorial_Time)) +
  geom_bar(stat="identity", fill="steelblue") +
  ggtitle('Average Tutorial Time by Video Game Experience') +
  xlab('Video Game Experience') +
  ylab('Average Time (seconds)')
ggsave(filename = "visualized/video_game_exp_vs_tut.png", plot = plot, width = 5, height = 2, dpi = 500)
plot


plot <- ggplot(video_game_exp_stats, aes(x=Video_game_exp, y=Avg_Task_Time)) +
  geom_bar(stat="identity", fill="steelblue") +
  ggtitle('Average Task Time by Video Game Experience') +
  xlab('Video Game Experience') +
  ylab('Average Time (seconds)')
ggsave(filename = "visualized/video_game_exp_vs_task.png", plot = plot, width = 5, height = 2, dpi = 500)
plot

# VR Experience
plot <- ggplot(vr_exp_stats, aes(x=VR_exp, y=Avg_Tutorial_Time)) +
  geom_bar(stat="identity", fill="steelblue") +
  ggtitle('Average Tutorial Time by VR Experience') +
  xlab('VR Experience') +
  ylab('Average Time (seconds)')
ggsave(filename = "visualized/vr_exp_vs_tut.png", plot = plot, width = 5, height = 2, dpi = 500)
plot

plot <- ggplot(vr_exp_stats, aes(x=VR_exp, y=Avg_Task_Time)) +
  geom_bar(stat="identity", fill="steelblue") +
  ggtitle('Average Task Time by VR Experience') +
  xlab('VR Experience') +
  ylab('Average Time (seconds)')
ggsave(filename = "visualized/r_exp_vs_task.png", plot = plot, width = 5, height = 2, dpi = 500)
plot

# Background in Design/Tech
plot <- ggplot(background_exp_stats, aes(x=Background_design_tech, y=Avg_Tutorial_Time)) +
  geom_bar(stat="identity", fill="steelblue") +
  ggtitle('Average Tutorial Time by Background in Design/Tech') +
  xlab('Background in Design/Tech') +
  ylab('Average Time (seconds)')
ggsave(filename = "visualized/background_vs_tut.png", plot = plot, width = 5, height = 2, dpi = 500)
plot

plot <- ggplot(background_exp_stats, aes(x=Background_design_tech, y=Avg_Task_Time)) +
  geom_bar(stat="identity", fill="steelblue") +
  ggtitle('Average Task Time by Background in Design/Tech') +
  xlab('Background in Design/Tech') +
  ylab('Average Time (seconds)')
ggsave(filename = "visualized/background_vs_task.png", plot = plot, width = 5, height = 2, dpi = 500)
plot

```

Based on the preference Likert scale, number of people who think Flat UI is good is slightly greater than 3D UI.





playthrough time boxplot
```{r}
library(reshape2)

selected_columns <- data[c("Tutorial_time", "Task_time")]

data_long <- melt(selected_columns)

library("ggpubr")
plot <- ggboxplot(data_long, x = "variable", y = "value",
          color = "variable",
          order = c("Tutorial_time", "Task_time"),
          ylab = "Time to Complete", xlab = "Playthrough")

ggsave(filename = "visualized/playthrough_time_boxplot.png", plot = plot, width = 5, height = 4, dpi = 500)

plot
```

There are no significant outliers.






```{r}
library(ggplot2)

overall_pref_count <- table(data$Overall_preference)

# Converting the table to a dataframe for ggplot
df_overall_pref <- as.data.frame(overall_pref_count)

# Creating the pie chart
plot <- ggplot(df_overall_pref, aes(x = "", y = Freq, fill = Var1)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y") +
  labs(fill = "Overall Preference", 
       title = "Distribution of Overall Preferences") +
  theme_void()


ggsave(filename = "visualized/overall_preference_distribution.png", plot = plot, width = 5, height = 4, dpi = 500)

plot
```

Even though more people think Flat UI is better to interact with, but they still prefer 3D UI more than Flat UI.




Below are the Kruskal-Wallis test. All no significant difference (P Value > 0.005), which means video game experience, VR experience, and background in design or tech does affect the overall performance.
```{r}
kruskal_result <- kruskal.test(Task_time ~ VR_exp, data = data)
kruskal_result
```


```{r}
kruskal_result <- kruskal.test(Task_time ~ Video_game_exp, data = data)
kruskal_result
```


```{r}
kruskal_result <- kruskal.test(Task_time ~ Background_design_tech, data = data)
kruskal_result
```


```{r}
kruskal_result <- kruskal.test(Tutorial_time ~ VR_exp, data = data)
kruskal_result
```


```{r}
kruskal_result <- kruskal.test(Tutorial_time ~ Video_game_exp, data = data)
kruskal_result
```


```{r}
kruskal_result <- kruskal.test(Tutorial_time ~ Background_design_tech, data = data)
kruskal_result
```

